Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-04-03 paper/propane.tex
final edits
implemented export policy translation for quagga

\begin{code}
\Define Ownership = 
    \{PG1 \Path \End(A)
     PG2 \Path \End(B)
     PL1 \Path \End(E)
     PL2 \Path \End(F)\}
\end{code}
\noindent
In English: traffic for prefix \CD{PG1} is only allowed to follow paths that
end at router \CD{A}; traffic matching \CD{PG2},
but not \CD{PG1}, must
end at router \CD{B}; and so on.
For the second constraint, we can define another policy:

%% \begin{lstlisting}[mathescape=true]
%% define Routing = {
%%     $\path{p_{g*}}{any}$
%%     $\path{p_{l*}}{\NOT enter(out)}$
%%     $\path{true}{exit(out)}$
%% }
%% \end{lstlisting}
\begin{code}
\Define Routing = 
    \{PG1 \OR PG2 \Path \Any
     PL1 \OR PL2 \Path \NOT{}\Enter(\Out)
     \True      \Path \Exit(\Out)\}
\end{code}
\noindent
The first line states that there is no restriction (\Any)
on how traffic must traverse the network for global prefixes.
%aside from the default restriction
%that traffic must not pass through the user's network and then loop
%back on itself. 
This means traffic for
\CD{PG*} may be sent either from other data center routers or
from external ASes. The second line ensures that traffic for local
prefixes never enters the network from an outside location. This constraint
guarantees that the services remain reachable only to locations
inside the data center.

As in the backbone example, we can logically conjoin these constraints
to specify the network-wide policy.
However, in addition to constraints on the shape of paths,
\sysname allows the operator to specify constraints on the BGP control plane.
For instance, a constraint on aggregation is included to ensure that
aggregation for global prefixes is performed from
locations inside (\In) the network to locations outside (\Out). 
In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG} 
(which we assume is defined earlier using an appropriate prefix such 
as \CD{74.3.28.0/24})
when advertised outside the datacenter.

\begin{code}
Ownership \AND{} Routing \AND{} \Agg(PG, \In \Link \Out)
\end{code}

>>>>

\begin{code}
\Define Ownership = 
    \{PG1 \Path \End(A)
     PG2 \Path \End(B)
     PL1 \Path \End(E)
     PL2 \Path \End(F)
     \True \Path \End(\Out)\}
\end{code}
\noindent
In English: traffic for prefix \CD{PG1} is only allowed to follow paths that
end at router \CD{A}; traffic matching \CD{PG2},
but not \CD{PG1}, must
end at router \CD{B}; and so on.
Any traffic destined for a prefix that not a part of the data center should be allowed to leave the data center and end at some external location.
For the second constraint, we can define another policy:

%% \begin{lstlisting}[mathescape=true]
%% define Routing = {
%%     $\path{p_{g*}}{any}$
%%     $\path{p_{l*}}{\NOT enter(out)}$
%%     $\path{true}{exit(out)}$
%% }
%% \end{lstlisting}
\begin{code}
\Define Locality = 
    \{PL1 \OR PL2 \Path \textbf{only}(\In)\}
\end{code}
\noindent
%The first line states that there is no restriction (\Any)
%on how traffic must traverse the network for global prefixes.
%aside from the default restriction
%that traffic must not pass through the user's network and then loop
%back on itself. 
%This means traffic for
%\CD{PG*} may be sent either from other data center routers or
%from external ASes. 
The locality constraint ensures that traffic for local
prefixes only ever follows paths that are internal to the network at each hop. 
This constraint guarantees that the services remain reachable only to locations
inside the data center.

As in the backbone example, we can logically conjoin these constraints
to specify the network-wide policy.
In addition to constraints on the shape of paths,
\sysname allows the operator to specify constraints on the BGP control plane.
For instance, a constraint on aggregation is included to ensure that
aggregation for global prefixes is performed from
locations inside (\In) the network to locations outside (\Out). 
In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG} 
(which we assume is defined earlier using an appropriate prefix such 
as \CD{74.3.28.0/24})
when advertised outside the datacenter.

\begin{code}
Ownership \AND{} Locality \AND{} \Agg(PG, \In \Link \Out)
\end{code}
